Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2020-12-27 NEUROC/sec4-experiments.tex

The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} was valid for both training and inference.
%
Fixing other hyper-parameters, each hyper-parameter itself affected the training/inference time and the memory usage of a GNN layer \emph{in a linear way}.
%
Algorithm engineers could adjust hyper-parameters according to the complexity analysis to avoid explosive growth in training/inference time and memory usage.
%
The accuracy of GNNs was much more sensitive to the dimensions of hidden vectors/heads than the other hyper-parameters.
%
The relative accuracy between GNNs varied greatly with different datasets.
%
Simple GNN models (such as GCN) could achieve good accuracy with proper hyper-parameter settings.

>>>>

The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} was valid for both training and inference.
%
Fixing other hyper-parameters, each hyper-parameter itself affected the training/inference time and the memory usage of a GNN layer \emph{in a linear way}.
%
Algorithm engineers could adjust hyper-parameters according to the complexity analysis to avoid explosive growth in the training/inference time and memory usage.
%
The accuracy of GNNs was much more sensitive to the dimension of hidden vectors/heads than the other hyper-parameters.
%
The relative accuracy between GNNs varied greatly with different datasets.
%
Simple GNN models (such as GCN) could achieve good accuracy with proper hyper-parameter settings.
